### 2018-04-17 paper/algorithm.tex
Fixes a broken \cref
Adds figures with algorithmic overviews

@@

On one hand, a user's devices must exchange information among themselves to learn the user's behavior \commentAL{Can we skip files mapping, pretty please?} and map files to devices.
We call this part of the protocol the \localoverlay, and present it in 
\cref{local-overlay}. On the other hand, user's collectively upload the list of 
their connected devices and associated future predictions to a Distributed Hash 
Table (DHT): it serves as a registry of online peers (including connection 
probabilities for the next turn), and for the routing of files.
We describe this \globaloverlay in \cref{global-overlay}. File exchange between 
two users is enabled by the two previous protocols, and is covered in \cref{file 
  exchange}

>>>>

\NewScheme{\SPOR}{SPOR}
\NewAlgorithm{\Send}{Send}
\NewAlgorithm{\Recv}{Receive}

\NewVariable{\rdv}{rdv}
\NewAlgorithm{\Enc}{Enc}
\NewVariable{\pk}{pk}
\NewAlgorithm{\Fwd}{Forward}
\NewAlgorithm{\Dec}{Dec}
\NewVariable{\sk}{sk}

We have the Secure Probabilistic Onion Routing scheme, \SPOR, which provides 
onion-routed message passing.
\(\SPOR\) provides two algorithms: \(\SPOR[\Send]\) (\cref{SPORSend}), 
\(\SPOR[\Fwd]\) (\cref{SPORFwd}) and \(\SPOR[\Recv]\) (\cref{SPORRecv}).

\NewAlgorithm{\ExtendRoute}{ExtendRoute}
\NewAlgorithm{\GetRouteNode}{GetRouteNode}
\NewAlgorithm{\GetRandomPeer}{GetRandomPeer}

\begin{figure}
  \begin{algorithmic}
    \Require{%
      $D$ is the set of alternative destination devices,
      $L$ is the length of the route,
      $\theta$ is the threshold of probability of failure.%
    }
    \Function{\ExtendRoute}{$H, L, \theta$}
      \If{$L\leq 0$}
        \State \Return $H$
      \EndIf
      \State $D\gets \GetRouteNode[\theta]$
      \State $H\gets D\concat \Enc[_{\pk_{D}}][H]$
      \State \Return $\ExtendRoute[H, L-1, \theta]$
    \EndFunction

    \Function{\GetRouteNode}{$\theta$}
      \State $D\gets \GetRandomPeer$
      \While{$\prod_{d\in D} \Pr[d \text{ offline}] > \theta$}
        \State $D\gets D\cup \GetRandomPeer$
      \EndWhile
      \State \Return $D$
    \EndFunction
  \end{algorithmic}
  \caption{%
    The function \(\ExtendRoute\) extends a route with \(L\) hops and failure 
    threshold of \(\theta\) for each hop in the route.
    Thus the probability of failure for the whole route is \(1 - (1 - 
      \theta)^L\).
    The function \(\GetRandomPeer\) is any random peer-sampling algorithm.
  }
\end{figure}

\begin{figure}
  \begin{algorithmic}
    \Require{%
      $D$ is the set of alternative recipient devices.
    }
    \Function{\SPOR[\Recv]}{$D$}
      \State $H_\rdv\gets \ExtendRoute[D\concat \bot, L, \theta]$
      \State Give $H_\rdv$ to sender out-of-bound.
      \State Wait to receive message.
    \EndFunction
  \end{algorithmic}
  \caption{\label{SPORRecv}%
    The recipient function.%
  }
\end{figure}

\begin{figure}
  \begin{algorithmic}
    \Require{%
      $m$ is the message to be sent,
      $H_\rdv$ is the onion-route given by the recipient (its first node is the 
      rendez-vous point).
    }
    \Function{\SPOR[\Send]}{$m, H_\rdv$}
    \EndFunction
  \end{algorithmic}
  \caption{\label{SPORSend}%
    The algorithm for creating a probabilistic onion route.
    \(d\) is the destination address, \(m\) is the message, \(H_\rdv\) is the 
    header for the rendez-vous point selected by \(d\).%
  }
\end{figure}

\begin{figure}
  \begin{algorithmic}
    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
    \Function{\SPOR[\Fwd]}{$C_H$}
      \State $H\gets \Dec[_\sk][C_H]$
      \If{$H = \bot$}
        \State \Return $\bot$
      \EndIf
      \State $\{d_i\}\concat H'\gets H$
      \For{$d\in \{d_i\}$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[H'] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}
  \caption{\label{SPORFwd}%
    The forwarding function for a node in a probabilistic onion route.%
  }
\end{figure}

@@

On one hand, a user's devices must exchange information among themselves to learn the user's behavior \commentAL{Can we skip files mapping, pretty please?} and map files to devices.
We call this part of the protocol the \localoverlay, and present it in 
\cref{local-overlay}. On the other hand, user's collectively upload the list of 
their connected devices and associated future predictions to a Distributed Hash 
Table (DHT): it serves as a registry of online peers (including connection 
probabilities for the next turn), and for the routing of files.
We describe this \globaloverlay in \cref{global-overlay}. File exchange between 
two users is enabled by the two previous protocols, and is covered in 
\cref{file-exchange}
